A sensor grid approach for large scale acoustic monitoring

### 2017-06-26 paper/article.tex
done with ininti...

Intelligibility in decoded and reconstructed audio is also an important concern in this study. It is indeed important that the proposed scheme ensures a high level of recognition of acoustic events but, as the data is transmitted over the network and potentially stored, the level of intelligibility of the decoded stream should be as low as possible.

Forensic phonetics \cite{baldwin1990forensic}

indice biométrique faible \cite{boe2000forensic}

In order to decrease the intelligibility, several approaches can be considered. First,  a speech versus non speech detector can be implemented on the sensor. If some speech is detected, the data is not transmitted. This approach is prone to failure of the detector and will lead to unavailibility of data whcih might compromise the computation of some indicators. Second, as the speech is mostly concentrated at a given frequency region, a band pass filter from 1 kHz to $~$4-5 kHz could be considered in order to remove the formant information \cite{kent1992acoustic}. However, as some frequency bands are no longer available, the computation of the acoustic indicators is no longer possible. A third approach is to wisely choose the frame rate. Since a phoneme is about 100ms to 200ms long \cite{kuwabara1996acoustic} \cite{rosen1992temporal} a frame rate lower than 4 Hz should dramatically reduce intelligibility.

>>>>

Intelligibility in decoded and reconstructed audio is also an important concernof this study. It is indeed important that the proposed scheme ensures a high level of recognition of acoustic events but, as the data is transmitted over the network and potentially stored, the level of intelligibility of the decoded stream should be as low as possible.

The use of an audio recording as an evidence is considered by the forensic phonetics \cite{baldwin1990forensic} domain. It shall be remebered that even recorded with a good quality, such recording remains a weak biometrical indicator \cite{boe2000forensic}. Still, even if the identity of the speaker cannot be asserted, one can attempt to transcribe the spoken utterances. As such, we believe that it is important to demonstrate that the proposed encoding scheme do not allow such thing.

In order to decrease the intelligibility, several approaches can be considered. First,  a speech versus non speech detector can be implemented on the sensor. If some speech is detected, the data is not transmitted. This approach is however prone to failure of the detector and will lead to unavailibility of data during speech time periods which might compromise the computation of some indicators.

Second, as the speech is mostly concentrated at a given frequency region, a band pass filter from 1 kHz to $~$4-5 kHz could be considered in order to remove the formant information \cite{kent1992acoustic}. However, as some frequency bands are no longer available, the computation of the acoustic indicators is no longer possible.

A third approach is to wisely choose the frame rate. Since a phoneme is about 100ms to 200ms long \cite{kuwabara1996acoustic} \cite{rosen1992temporal} a frame rate lower than 4 Hz should therefore dramatically reduce intelligibility.
